ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2016-07-29 asce-paper.tex
more we's, final pass

Often, there is no failure data for the system itself
(e.g., if the system is a prototype, or the system is used under unique circumstances),
but there is some information about failure times for the components the system is made of.
The proposed method allows to analyse systems of arbitrary system structures, %layout of components,
i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
by use of the survival signature \cite{2012:survsign}.
In this paper, we assume that components can be divided into $K$ different groups,
and components within each group $k$ ($k=1, \ldots, K$) can be assumed to be exchangeable,
i.e., to follow the same failure time distribution.
Components of group $k$ are denoted as \emph{type $k$ components},
and are assumed to be independent from components of other types.
%such that failure times of components of different types are independent.
Type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
are assumed as Weibull distributed with type-specific parameters,
where the shape parameter $\beta_k$ is known
and the scale parameter $\lambda_k$ is unknown.

@@

This work extends \ldots ***

***general methods (sets of conjugate priors, survival signature)
can be used with other parametric component lifetime distributions
that form a canonical exponential family
(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}),
such that conjugate prior can be constructed***

***We study the effect of surprisingly early or late component failures,
%on the system reliability prediction,
showing that observations in conflict to prior assumptions
indeed lead to more cautious system reliability predictions.***

The paper is organized as follows.
In Section~\ref{sec:weibull}, we describe a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter
and illustrate the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this mitigates the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
for a running system based on sets of priors for $\lambda_k$. 
%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
%is transfomed to the necessary form for use within the survival signature framework,
%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
Section~\ref{sec:elicitation} discusses elicitation,
by giving guidelines on how to choose prior parameter bounds
that reflect expert information on components;
Section~\ref{sec:examples} contains examples illustrating the merits of our method.
Section~\ref{sec:concluding} concludes the paper by *** 
***

@@

We consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.

@@

The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
we need to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\label{eq:ig-def}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

@@

However, the weighted average structure for $\yn$
is behind the problematic behaviour in case of prior-data conflict.
Assume that from expert knowledge we expect
to have a mean component lifetime of 9 weeks.
Using \eqref{eq:lambdainterpret}, with $\beta=2$ we obtain $\yz = 103.13$.
We choose $\nz = 2$, so our prior guess for the mean component lifetime
counts like having two observations with this mean.
If we now have a sample of two observations
with surprisingly early failure times $t_1 = 1$ and $t_2 = 2$,
using \eqref{eq:ig-update} we get $\nfun{2} = 4$
and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
so our posterior expectation for the scale parameter $\lambda$ is $52.82$,
equivalent to a mean component lifetime of $6.44$ weeks.
The posterior standard deviation (sd) for $\lambda$ is $60.99$.
Compared to the prior standard deviation of $145.85$,
the posterior expresses now more confidence that mean lifetimes are around $\yfun{2} = 52.82$
than the prior had about $\yz = 103.13$.
This irritating conclusion is illustrated in Figure~\ref{fig:weibull-pdc};
the posterior cdf is shifted halfway towards the values for $\lambda$
that the two observations suggest
(the ML estimator for $\lambda$ would be $2.5$),
and is steeper than the prior (so the pdf is more pointed),
thus conveying a false sense of certainty about $\lambda$.%
\footnote{This is a general problem in Bayesian analysis with canonical conjugate priors.
For such priors, the same update formula \eqref{eq:ig-update} applies,
and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.}
We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
posterior distribution
if we had assumed the mean component lifetime to be 7 weeks (so $\yz = 62.39$),
and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.
%
%\iffalse
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{fig1}
\caption{Prior and posterior cdf for $\lambda$ given surprising observations;
the conflict between prior assumptions and data is averaged out,
with a more pointed posterior giving a false sense of certainty.}
\label{fig:weibull-pdc}
\end{figure}
%\fi

@@

Continuing the example from Section~\ref{sec:weibull} and Figure~\ref{fig:weibull-pdc},
assume now for the mean component lifetimes the range 9 to 11 weeks,
this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
We also choose $[\nzl,\nzu] =[2, 5]$,
so we value our prior information as equivalent to having seen two to five observations.
Compare now the set of posteriors obtained from observing
$t_1 = 1$, $t_2 = 2$ (as before), see Figure~\ref{fig:setofpost-pdc-nopdc} (left),
and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
We now have a clear difference between the two scenarios of
observations in line with expectations and observations in conflict.
In the prior-data conflict case, the set of posteriors (blue)
is shifted towards the left, but has about the same size as the set of priors (yellow),
and so posterior quantification of reliability has the same precision,
despite having seen two observations.
Instead, in the no conflict case, the set of posteriors is smaller than the set of priors,
such that the two observations have increased the precision of reliability statements.

@@

We now consider a system of arbitrary layout,
consisting of components of $K$ types.
This system is observed until time $\tnow$,
leading to censored observation of lifetimes of components within the system,
and we will explain in Section~\ref{sec:lambdawithcens}
how the scale parameter $\lambda_k$ for component type $k$
can be estimated in this situation.
%
Section~\ref{sec:sysrelwithsurvsign} describes then
how the system reliability function can be efficiently obtained using the survival signature.
%
For this, we need the posterior predictive distribution
of the number of components that function at times $t > \tnow$,
which we will derive in Section~\ref{sec:postpred}.
%
Finally, in Section~\ref{sec:optimize} we describe how
the lower and upper bound for the system reliability function
are obtained when prior parameters $(\nkz,\ykz)$
vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
defining sets $\MkZ$ of prior distributions over $\lambda_k$,
as introduced in Section~\ref{sec:modforsurpr}.

@@

    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k

@@

Now, by the Weibull assumption \eqref{eq:weibullcdf}, we have

@@

With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, we get

@@

allowing us to solve the integral using the corresponding normalization constant.

@@

Together with \eqref{eq:postpred-priorparams},
\eqref{eq:sysrel-survsign} allows us to calculate the system reliability $\Rsys(t\mid t>\tnow)$
for fixed prior parameters $(\nkz, \ykz)$, $k=1, \ldots, K$.
In Section~\ref{sec:modforsurpr}, we argued for using sets of priors $\MZ$,
which allow for vague and incomplete prior knowledge, and provide prior-data conflict sensitivity.
%
We will thus use, for each component type,
a set of priors $\MkZ$ defined by varying $(\nkz,\ykz)$ in a prior parameter set $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
and we are interested in the bounds
%This leads to a set of system reliability functions with the bounds
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow) &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
\label{eq:lrsysdef}\\
\uRsys(t \mid t > \tnow) &= \max_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
\label{eq:ursysdef}
\end{align}
\end{linenomath*}
where we surpress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
depend on prior parameter sets and data.

\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
a full $2K$-dimensional box-constraint optimization is necessary,
but this is not the case.
Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
then there is, for each component type $k$,
a prior parameter pair in $\PkZ$ that minimizes system reliability, and
a prior parameter pair in $\PkZ$ that maximizes system reliability,
independently of the other component types. 
%such that system reliability is
%minimized by a distribution that gives most weight to low values of $l_k$, and
%maximized by a distribution that gives most weight to high values of $l_k$.
Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
which in turn increases the probability that many components survive until time $t$,
and with it, decreases the propability of few or no components surviving,
so in total giving low probability weight for low values of $l_k$,
and high probability weight for high values of $l_k$. 
We therefore conclude that, for any fixed value of $\nkz$,
the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.

%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
%but not for posterior predictive***
%
However, there is no corresponding reasoning for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

Writing out \eqref{eq:sysrel-survsign}, we get
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\label{eq:sysrel-optim-n0}
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.

@@

We have implemented the method in \textsf{R},
using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim},
and pan to release a package containing the code to reproduce all results and figures
for the examples in Section~\ref{sec:examples}.

@@

To represent expert knowledge on component failure times
through bounds for $\ykz$ and $\nkz$,
we can refer to the interpretations as given in Section~\ref{sec:weibull}:
$\ykz$ is the prior expected value of $\lambda_k$,
where $\lambda_k$ is linked to expected component lifetimes through \eqref{eq:lambdainterpret}.
$\nkz$ can be seen as pseudocount, indicating how strong expert knwoledge is trusted
in comparison to a sample of size $n$.
Our approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
instead of forcing a precise answer.

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig4}
\caption{Sets of prior predictive reliability functions for the four component types,
illustrating the choice of prior parameter sets $\PkZ$.}
\label{fig:brake-comppriors}
\end{figure}

>>>>

Often, there is no failure data for the system itself
(e.g., if the system is a prototype, or the system is used under unique circumstances),
but there is some information about failure times for the components the system is made of.
The proposed method allows to analyse systems of arbitrary system structures, %layout of components,
i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
by use of the survival signature \cite{2012:survsign}.
In doing so, the present paper extends similar previous work
which focused on a simple parallel system with homogeneous components \cite{2015:walter}.
In this paper, we assume that components can be divided into $K$ different groups,
and components within each group $k$ ($k=1, \ldots, K$) can be assumed to be exchangeable,
i.e., to follow the same failure time distribution.
Components of group $k$ are denoted as \emph{type $k$ components},
and are assumed to be independent from components of other types.
%such that failure times of components of different types are independent.
Type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
are assumed as Weibull distributed with type-specific parameters,
where the shape parameter $\beta_k$ is known
and the scale parameter $\lambda_k$ is unknown.

@@

The paper is organized as follows.
In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter is describe,
illustrating the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this mitigates the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
for a running system based on sets of priors for $\lambda_k$. 
%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
%is transfomed to the necessary form for use within the survival signature framework,
%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
Section~\ref{sec:elicitation} discusses elicitation,
by giving guidelines on how to choose prior parameter bounds
that reflect expert information on components.
Section~\ref{sec:examples} contains examples illustrating the merits of our method,
by studying the effect of surprisingly early or late component failures,
showing that observations in conflict to prior assumptions
indeed lead to more cautious system reliability predictions.
Section~\ref{sec:concluding} concludes the paper by summarizing results
and indicating avenues for further research.

@@

Consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.

@@

The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
one needs to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\label{eq:ig-def}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

@@

However, the weighted average structure for $\yn$
is behind the problematic behaviour in case of prior-data conflict.
Assume that from expert knowledge we expect
to have a mean component lifetime of 9 weeks.
Using \eqref{eq:lambdainterpret}, with $\beta=2$ we obtain $\yz = 103.13$.
We choose $\nz = 2$, so our prior guess for the mean component lifetime
counts like having two observations with this mean.
If we now have a sample of two observations
with surprisingly early failure times $t_1 = 1$ and $t_2 = 2$,
using \eqref{eq:ig-update} we get $\nfun{2} = 4$
and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
so our posterior expectation for the scale parameter $\lambda$ is $52.82$,
equivalent to a mean component lifetime of $6.44$ weeks.
The posterior standard deviation (sd) for $\lambda$ is $60.99$.
Compared to the prior standard deviation of $145.85$,
the posterior expresses now more confidence that mean lifetimes are around $\yfun{2} = 52.82$
than the prior had about $\yz = 103.13$.
This irritating conclusion is illustrated in Figure~\ref{fig:weibull-pdc};
the posterior cdf is shifted halfway towards the values for $\lambda$
that the two observations suggest
(the ML estimator for $\lambda$ would be $2.5$),
and is steeper than the prior (so the pdf is more pointed),
thus conveying a false sense of certainty about $\lambda$.
We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
posterior distribution
if we had assumed the mean component lifetime to be 7 weeks (so $\yz = 62.39$),
and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.

Note that this is a general problem in Bayesian analysis with canonical conjugate priors.
For such priors, the same update formula \eqref{eq:ig-update} applies,
and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.
%
%\iffalse
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{fig1}
\caption{Prior and posterior cdf for $\lambda$ given surprising observations;
the conflict between prior assumptions and data is averaged out,
with a more pointed posterior giving a false sense of certainty.}
\label{fig:weibull-pdc}
\end{figure}
%\fi

@@

Continuing the example from Section~\ref{sec:weibull} and Figure~\ref{fig:weibull-pdc},
assume now for the mean component lifetimes the range 9 to 11 weeks,
this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
Choosing $[\nzl,\nzu] =[2, 5]$
means to value this information on mean component lifetimes as equivalent to having seen two to five observations.
Compare now the set of posteriors obtained from observing
$t_1 = 1$, $t_2 = 2$ (as before), see Figure~\ref{fig:setofpost-pdc-nopdc} (left),
and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
There is now a clear difference between the two scenarios of
observations in line with expectations and observations in conflict.
In the prior-data conflict case, the set of posteriors (blue)
is shifted towards the left, but has about the same size as the set of priors (yellow),
and so posterior quantification of reliability has the same precision,
despite having seen two observations.
Instead, in the no conflict case, the set of posteriors is smaller than the set of priors,
such that the two observations have increased the precision of reliability statements.

@@

Consider now a system of arbitrary layout,
consisting of components of $K$ types.
This system is observed until time $\tnow$,
leading to censored observation of lifetimes of components within the system,
and we will explain in Section~\ref{sec:lambdawithcens}
how the scale parameter $\lambda_k$ for component type $k$
can be estimated in this situation.
%
Section~\ref{sec:sysrelwithsurvsign} describes then
how the system reliability function can be efficiently obtained using the survival signature.
%
For this, we need the posterior predictive distribution
of the number of components that function at times $t > \tnow$,
which we will derive in Section~\ref{sec:postpred}.
%
Finally, in Section~\ref{sec:optimize} we describe how
the lower and upper bound for the system reliability function
are obtained when prior parameters $(\nkz,\ykz)$
vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
defining sets $\MkZ$ of prior distributions over $\lambda_k$,
as introduced in Section~\ref{sec:modforsurpr}.

@@

    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k\,.

@@

Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has

@@

With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, this gives

@@

allowing to solve the integral using the corresponding normalization constant.

@@

Together with \eqref{eq:postpred-priorparams},
\eqref{eq:sysrel-survsign} allows to calculate the system reliability $\Rsys(t\mid t>\tnow)$
for fixed prior parameters $(\nkz, \ykz)$, $k=1, \ldots, K$.
In Section~\ref{sec:modforsurpr}, we argued for using sets of priors $\MZ$,
which allow for vague and incomplete prior knowledge, and provide prior-data conflict sensitivity.
%
We will thus use, for each component type,
a set of priors $\MkZ$ defined by varying $(\nkz,\ykz)$ in a prior parameter set $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
and the objective is to obtain the bounds
%This leads to a set of system reliability functions with the bounds
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow) &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
\label{eq:lrsysdef}\\
\uRsys(t \mid t > \tnow) &= \max_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
\label{eq:ursysdef}
\end{align}
\end{linenomath*}
where we suppress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
depend on prior parameter sets and data.

\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
a full $2K$-dimensional box-constraint optimization is necessary,
but this is not the case.
Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
then there is, for each component type $k$,
a prior parameter pair in $\PkZ$ that minimizes system reliability, and
a prior parameter pair in $\PkZ$ that maximizes system reliability,
independently of the other component types. 
%such that system reliability is
%minimized by a distribution that gives most weight to low values of $l_k$, and
%maximized by a distribution that gives most weight to high values of $l_k$.
Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
which in turn increases the probability that many components survive until time $t$,
and with it, decreases the propability of few or no components surviving,
so in total giving low probability weight for low values of $l_k$,
and high probability weight for high values of $l_k$. 
Therefore, for any fixed value of $\nkz$, 
the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
%
%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
%but not for posterior predictive***
%
There is however no corresponding result for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

Writing out \eqref{eq:sysrel-survsign}, one obtains
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\label{eq:sysrel-optim-n0}
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.

@@

We have implemented the method in the statistical computing environment \textsf{R} \cite{R},
using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim},
and intend to release a package containing functions and code to reproduce all results and figures
for the examples in Section~\ref{sec:examples} below.

@@

To represent expert knowledge on component failure times
through bounds for $\ykz$ and $\nkz$,
one can refer to the interpretations as given in Section~\ref{sec:weibull}:
$\ykz$ is the prior expected value of $\lambda_k$,
where $\lambda_k$ is linked to expected component lifetimes through \eqref{eq:lambdainterpret}.
$\nkz$ can be seen as pseudocount, indicating how strong expert knowledge is trusted
in comparison to a sample of size $n$.
Crucially, the approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
instead of requiring a precise answer.

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig4}
\caption{Sets of prior predictive reliability functions for the four component types,
illustrating the choice of prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$.}
\label{fig:brake-comppriors}
\end{figure}
